Untitled

### 2020-04-23 paper_results.Rmd
update

  library(tidyverse)
  library(mixor)
  library(sjPlot)
  library(viridis)

@@

  table_1_df <- select(patients, 
    age, gender, diag, comorbid, meds, cfs, must_screen, must_score, 
    dementia:paralysis, restrict_diet, modified_diet, diet_ref, diet_plan
    )

@@

```{r table_1}

  data_frame(
    Variable = name.1(table_1_df),
    Missing   = n.miss(table_1_df),
    "Mean SD" = summary.1(table_1_df),
    "Median [IQR]" = med.iqr(table_1_df),
    "(Min, Max)" = min.max(table_1_df)
    ) %>% 
  knitr::kable()

@@

>>>>

  library(tidyverse)
  library(mixor)
  library(sjPlot)
  library(viridis)
  library(flextable)

@@

  table_1_df <- select(patients, 
    age, gender, patient_type, comorbid, meds, cfs, must_screen, must_score, 
    dementia:paralysis, restrict_diet, modified_diet, diet_ref, diet_plan, 
    redtray
    )

@@

```{r table_1_h, eval = knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}

# Table 1 for .md or .html
  data_frame(
    Variable = name.1(table_1_df),
    Missing   = n.miss(table_1_df),
    "Mean SD" = summary.1(table_1_df),
    "Median [IQR]" = med.iqr(table_1_df),
    "(Min, Max)" = min.max(table_1_df)
    ) %>% 
  flextable()

```{r table_1_w, eval = !knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}

# Table 1 for .docx
  data_frame(
    Variable = name.1(table_1_df),
    Missing   = n.miss(table_1_df),
    "Mean SD" = summary.1(table_1_df),
    "Median [IQR]" = med.iqr(table_1_df),
    "(Min, Max)" = min.max(table_1_df)
    ) %>% 
  knitr::kable()

@@

```{r table_2_variables}

# See table 2 from Corina's draft, p12

  table_2_df <- select(patients, 
    age, gender, patient_type, comorbid, meds, cfs, must_screen, must_score, 
    dementia:paralysis, restrict_diet, modified_diet, diet_ref, diet_plan, 
    redtray
    )

```{r table_2_h, eval = knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}

# Table 2 for .md or .html
  data_frame(
    Variable = name.1(table_2_df),
    Missing   = n.miss(table_2_df),
    "Mean SD" = summary.1(table_2_df),
    "Median [IQR]" = med.iqr(table_2_df),
    "(Min, Max)" = min.max(table_2_df)
    ) %>% 
  flextable()

```{r table_2_w, eval = !knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}

# Table 2 for .docx
  data_frame(
    Variable = name.1(table_2_df),
    Missing   = n.miss(table_2_df),
    "Mean SD" = summary.1(table_2_df),
    "Median [IQR]" = med.iqr(table_2_df),
    "(Min, Max)" = min.max(table_2_df)
    ) %>% 
  knitr::kable()
